Poseidon Adventure

### 2019-05-24 docs/index.Rmd
Update index.html with latest date and notes for cal current write to SS Rmd

<a href="https://sgaichas.github.io/poseidon-dev/CreateStockSynthesis.html" target="_blank">Sardines in the CalCurrent, input to SS functions, May 22, 2019</a>

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/CreateStockSynthesis.html" target="_blank">Sardines in the CalCurrent, input to SS functions: May 24, 2019</a> - now generalized to run for any species in the cal current with a unique species config file
